Peer-to-peer Browser Middleware for Communication and Consensus in an Unreliable Infrastructure

### 2015-12-07 research_class/workshop.tex
workshop.tex: spell check.

\subsection{Signalling Server}

@@

The Raft over WebRTC chat application is a single web page (\texttt{chat.html}). When a new Raft cluster is created, the browser connects to the signalling server's new channel endpoint (Figure~\ref{fig:raft_rtc_sequence}~[1]). This endpoint causes the server to create a new channel for PeerJS signaling (Figure~\ref{fig:raft_rtc_sequence}~[2]). Once this is complete the server responds to the browser with a redirect message that contains the new channel identifier in the query parameter and ``firstServer” in the fragment identifier to indicate that this is the very first Raft cluster node (Figure~\ref{fig:raft_rtc_sequence}~[3]).

@@

\begin{enumerate}
\item The \emph{seqAppend} operation operates on a specially structured key/value pair in the state machine map. The value of the pair is another associative map that contains a counter and list structure where the actual chat lines are accumulated. \emph{seqAppend} operations are sent with both a count and then new value to append.
\item When a \emph{seqAppend} operation is applied to the state machine and the count value in the command matches the counter in the state machine's value, then the new line in the request is added to the value list and the counter is incremented. If the count value does not match the counter then the the operation is not applied. In either case, a list is returned in the \texttt{clientRequestResponse} that contains two values: a boolean indicating whether the \emph{seqAppend} operation succeeded and a number indicating the current value of the counter.
\item The first time the \emph{seqAppend} operation is used on a non-existent key, the structure described above is created with the counter set to 0 and the list structure is created with the single value that was passed in the \emph{seqAppend} operation.\
\item Clients that call the \emph{seqAppend} operation should check the status value in the result list. If the status is false, then the client should retry the operation. Regardless of success of failure, then client should store the current value of the counter for the next \emph{seqAppend} call or retry.
\end{enumerate}

@@

\section*{Acknowledgements}

>>>>

\subsection{Signaling Server}

@@

The Raft over WebRTC chat application is a single web page (\texttt{chat.html}). When a new Raft cluster is created, the browser connects to the signaling server's new channel endpoint (Figure~\ref{fig:raft_rtc_sequence}~[1]). This endpoint causes the server to create a new channel for PeerJS signaling (Figure~\ref{fig:raft_rtc_sequence}~[2]). Once this is complete the server responds to the browser with a redirect message that contains the new channel identifier in the query parameter and ``firstServer” in the fragment identifier to indicate that this is the very first Raft cluster node (Figure~\ref{fig:raft_rtc_sequence}~[3]).

@@

\begin{enumerate}
\item The \emph{seqAppend} operation operates on a specially structured key/value pair in the state machine map. The value of the pair is another associative map that contains a counter and list structure where the actual chat lines are accumulated. \emph{seqAppend} operations are sent with both a count and then new value to append.
\item When a \emph{seqAppend} operation is applied to the state machine and the count value in the command matches the counter in the state machine's value, then the new line in the request is added to the value list and the counter is incremented. If the count value does not match the counter then the the operation is not applied. In either case, a list is returned in the \texttt{clientRequestResponse} that contains two values: a Boolean indicating whether the \emph{seqAppend} operation succeeded and a number indicating the current value of the counter.
\item The first time the \emph{seqAppend} operation is used on a non-existent key, the structure described above is created with the counter set to 0 and the list structure is created with the single value that was passed in the \emph{seqAppend} operation.\
\item Clients that call the \emph{seqAppend} operation should check the status value in the result list. If the status is false, then the client should retry the operation. Regardless of success of failure, then client should store the current value of the counter for the next \emph{seqAppend} call or retry.
\end{enumerate}

@@

\section*{Acknowledgments}
